Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/study.tex
fix enumerate
tidying on the study section

At the beginning of this project, we made the following hypotheses
about array programming idioms:
\begin{enumerate}
\item Loops over arrays mainly read from arrays with a static pattern
based on constant offsets from (base or dervied) induction variables;

\item Most loop-array computations of the previous form read
from arrays with a \emph{contiguous} pattern, \eg{}:
%
\begin{minted}{fortran}
do i = 1, n
  b(n) = (a(i) + a(i+1)) / 2.0
\end{minted}
%
\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the immediate
neighbours (offsets of 1 from the induction variables);

\item Many array computations are \emph{stencil computations}: an
  assignment whose right-hand side comprises array subscripts with
  neighbourhood indices and whose left-hand side is an
  neighbourhood-indexed array subscript (\eg{}, the classic five-point
  stencil);

@@

LHS affine & RHS neigh  & 23        & 0.02\% & 0 & 0.00\% \\\hline \hline

@@

\begin{minipage}{1\linewidth}

@@

\hspace{1em}

>>>>

\noindent
At the beginning of this project, we made the following hypotheses
about array programming idioms:
\begin{enumerate}[leftmargin=2em]
\item Computations involving loops over arrays are common, where an
  arrays are read from with a static pattern based on constant offsets
  from (base or dervied) induction variables;

\item Most loop-array computations of the previous form read
from arrays with a \emph{contiguous} pattern, \eg{}:
%
\begin{minted}{fortran}
  b(n) = a(i-1) + a(i) + a(i+1)
\end{minted}
%
\item Most loop-array computations of the previous form read
from arrays with a pattern that includes the origin index
or its immediate neighbours (offsets of 1 from the induction variables);

\item Many array computations are \emph{stencil computations}: an
  assignment whose right-hand side comprises array subscripts with
  neighbourhood indices and whose left-hand side is an
  neighbourhood-indexed array subscript (\eg{}, the Laplace operator);

@@

LHS affine & RHS neigh  & 23        & 0.02\% & 0 & 0.00\% \\\hline

@@

\begin{minipage}{0.48\linewidth}

@@

\vspace{2.4em}
\begin{minipage}{0.5\linewidth}
